---
title: "Stats in R Assignment"
author: "Alex Lucchesi"
date: "2023/05/30"
output: html_document
---

## Assignment
For today's assignment, you will be given a blank notebook and a link to the [Call of Duty Dataset](https://www.kaggle.com/datasets/beridzeg45/call-of-duty-reviews)
You will need to fill out the notebook and create your own code chunks to run code. Remember that we use this code without any quotation marks to create a code chunk:
'```{r}
'```
### Your Goal:

To receive credit for today's assignment, you will need to:

* Import the dataset
* Load the dataset into a tibble
* Mutate a new column
* Create a hypothesis regarding your data and communicate that hypothesis in a scientific method.
* Create a notebook that has markdown cells, explaining your code and process/thoughts. **Your markdown should be well thought out and reflect a thorough analysis.**
* Clean the data
* Explore the data (include visualizations)
* Create a statistical test and communicate the results
```{r}
#imports
library(tidyverse)
library(dplyr)
library(conflicted)
dplyr::filter
```

```{r}
#read in the csv
df <- read.csv("/home/user/Documents/coding_temple/week7/day3/Call of Duty Reviews.csv")
df
```

```{r}
#tidy the columns, using lowercase and adding underscores
tidy <- function(n){
  names(n) <- names(n) %>% str_replace_all("\\.", "_")%>%tolower()
  return(n)
}
df <- tidy(df)
```

```{r}
#mutate the two compound score columns into a new average compound score between the two
df_mutate <- mutate(df,average_compound_score=((critic_compound_score+user_compound_score)/2))
df_mutate
```

```{r}
#Based on the data shown, a question could be asked that does the release year per each Call of Duty release have a direct correlation on the received metascore,
# considering different factors that may play a role in release year such as public attention and hype, Activision's promo budget different per year, etc

# the null hypothesis based on the data above is that, no, the release year does not have a direct correlation on the received metascore of the game.
# the alternative hypothesis would then be that the release year does indeed have a direct correlation on the received metascore of the game.
```

```{r}
# in order to test this, we must change the release year columns from character type to numeric first

df_mutate$release_year <- as.numeric(df_mutate$release_year)
df_mutate
```

```{r}
ggplot(data=df_mutate, mapping=aes(x=metascore, y=release_year, color=release_year))
```

```{r}
#performing correlation testing
correlation <- cor.test(df_mutate$release_year, df_mutate$metascore)
correlation
```

```{r}
ggplot(data=df_mutate) + geom_point(mapping=aes(x=metascore, y=release_year, color=release_year))
```

```{r}
correlation
```

```{r}
# The results showed that there was a -0.1975 correlation coefficient, showing there is a very weak negative correlation between metascore and the release year
# The resulted p-value is .0429, which is less than our alpha value of 0.05, showing that we would reject the null hypothesis in favor of the alternative hypothesis
```



