

### Homework

1.  Do 5 CodeWars problems in R. Share your solutions here:

    ```{r}
    # Problem 1 I solved in R:
    
      #Given an integral number, determine if it's a square number:
      #In mathematics, a square number or perfect square is an integer that is the square of an integer; in other words, it is the product of some integer with itself.
      #The tests will always use some integral number, so don't worry about that in dynamic typed languages.


    # Solution
    
    is_square <- function(n){
  if(n==0){TRUE} #check for 0's
  else if(n<0){FALSE} #check for negatives
  else(if((sqrt(n))/((sqrt(n))%/%1)!=1){FALSE}else{TRUE}) #check for perfect squares
    }
    
    #Problem 2 I solved in R:
      
      #Your code must return true or false (not 'true' and 'false') depending upon whether the given number is a Narcissistic number in base 10.
    
    # Solution
    
    armstrong <- function(num){
  if(num==(sum(as.numeric(strsplit(as.character(num),"")[[1]])^3)))
  {return (TRUE)}
  else{return(FALSE)}
    }
    # Problem 3 I solved in R:
      
      #Code as fast as you can! You need to double the integer and return it.
    
    # Solution
      double_integer <- function(i) {
  return(i*2)
}
      
    # Problem 4 I solved in R:
      
      #Complete the function so that it finds the average of the three scores passed to it and returns the letter value associated with that grade.
    
    # Solution
      get_grade <- function(a, b, c) {
   x <- ((a+b+c)/3)
   print(x)
   if(x<60){print('F')}
   else if(x>=60 & x<70){print('D')}
  else if(x>=70 & x<80){print('C')}
  else if(x>=80 & x<90){print('B')}
  else{print('A')}
  }
      
    # Problem 5 I solved in R:
      
      #Write a program that finds the summation of every number from 1 to num. The number will always be a positive integer greater than 0.
    
    # Solution
    summation <- function(n) {
  (n * (n + 1)) / 2
}
    ```

2.  Create a function that checks an input of type `int` and returns
    fizz if the number is a multiple of 3, buzz if the number is a
    multiple of 5, and fizzbuzz if the number is a multiple of 3 and 5.

    ```{r}
fizzchecker <- function(i){
  if((i/3)==(as.integer(i/3))){'fizz'}
  else if((i/5)==(as.integer(i/5))){'buzz'}
  else if((i/5 & i/3)==(as.integer(i/5 & i/3))){'fizzbuzz'}
  }
    
fizzchecker(10)
    ```

3.  **Mario Challenge:** In the classic Super Mario games, Mario ends
    each level by ascending a flight of stairs and leaping off the top
    to arrive at the castle at the end. (See
    [here](https://youtu.be/-avspZlbOWU?t=55) for details). We can
    imagine that each of the bricks of the stairs is a character X.
    Create a function that prints out a set of stairs. For example:

    If the function is called marioStairs() and we pass in the value 4,
    we would expect to see stairs with a length of 4 and a height of 4:

    X

    XX

    XXX

    XXXX

    ```{r}
    mariostairs <- function(i){
     for(x in 1:(i)){
        print(strrep("X",x))
      }
      
    }
mariostairs(4)
    ```

4.  Find a built-in dataset you would like to explore. Explore the
    dataset and use the cheat sheet you built in Week 1 to label
    continuous and discrete data. Analyze the dataset using dplyr,
    create graphs, mutate two columns, and formulate a hypothesis about
    your data.

#### **Data Types:**

-   Column 1: Data Type

-   Column 2: Data Type

```{r}
mtcars
```

```{r}
dplyr::glimpse(mtcars)
```

```{r}
colSums(is.na(mtcars))
```

```{r}
summary(mtcars)
```

```{r}
ggplot(data=mtcars) +
  geom_point(mapping = aes(hp,mpg))
```

```{r}
ggplot(data=mtcars) +
  geom_point(mapping = aes(hp,qsec))
```

#The plots were a good way of seeing if there was any time of correlation between miles per gallon and horsepower per vehicle, and even though the data shows not a very organized distribution, 
overall it seems to show that rising horsepower numbers generally have a negative correlation on fuel efficiency in most cars. There are outliers considering that many other characteristics
play a role in the development of the car. 
Another glimpse at a plot showed that horsepower and qsec had a stronger relationship, considering one affects the other in a more direct connection.